%______________________________________________________________________________________________________________________
% @brief    
\documentclass[margin,line]{resume}
\usepackage[colorlinks=true,urlcolor=blue]{hyperref}
\usepackage{nth}


\newlength\Colsep
\setlength\Colsep{10pt}


%______________________________________________________________________________________________________________________
\begin{document}
\name{\Large{Agnieszka Borowska} \hfill {\small 5th November 2021} \hspace{2.8cm}} 
\begin{resume}
%__________________________________________________________________________________________________________________
    % Contact Information
    \section{\mysidestyle Contact\\Information}
    University of Glasgow\hfill  E-mail: \url{Agnieszka.Borowska@glasgow.ac.uk} \\
    School of Mathematics and Statistics \hfill Website: \url{aborowska.github.io}\\ \vspace{0mm}%
    University Place \\
    Glasgow G12 8QQ\\ \vspace{-4.6mm}%    
%__________________________________________________________________________________________________________________
    % Research Interests
    \section{\mysidestyle Research\\Interests}
    
    Bayesian statistics, computational statistics, Monte Carlo methods, approximate Bayesian computations, time series, state space models, rare events
\vspace{-1mm}   
%__________________________________________________________________________________________________________________
 
    % Education
    \section{\mysidestyle Employment }
    \textbf{University of Glasgow},  UK \hfill from June 2020\\
	Research Associate in Statistics\\ 
    Position within the \href{https://www.gla.ac.uk/schools/computing/research/researchsections/ida-section/closedloop/}{Closed-Loop Data Science} project (an EPSRC funded project for Complex, Computationally- and Data-Intensive Analytic)
    (on leave Apr. -- Nov. 2021)
    \vspace{-2mm}

    \textbf{University of Glasgow},  UK \hfill  May 2018 -- May 2020\\
	Research Assistant in Statistics\\ 
    Position within the \href{http://softmech.org/}{SofTMech Centre} (an EPSRC centre for Multiscale Soft Tissue Mechanics)
    \vspace{-2mm}
        
    \textbf{VU Amsterdam},  The Netherlands \hfill Sep. 2015 -- Jul. 2019\\
	Ph.D. candidate in Econometrics  
    \vspace{-2mm}
    
    \textbf{Erasmus University Rotterdam},  The Netherlands \hfill Sep. 2014 -- Dec. 2014\\
	Teaching Assistant for graduate level courses\\ 
	
\vspace{-5mm}    
%__________________________________________________________________________________________________________________
    % Education
    \section{\mysidestyle Education}
    \textbf{VU Amsterdam} and \textbf{Tinbergen Institute},  The Netherlands \hfill Jul. 2019\\
	Ph.D. in Econometrics\\
	Title: \textit{Methods for Accurate and Efficient Bayesian Analysis of Time Series}\\ 
    Supervisors: Prof. Siem Jan Koopman and Dr Lennart Hoogerheide
\vspace{-2mm}

    \textbf{Tinbergen Institute} and \textbf{VU Amsterdam}, The Netherlands  \hfill Aug. 2015 	\\
	M.Phil.\ in Econometrics
	\vspace{-2mm}

	\textbf{University of Warsaw}, Poland  \hfill Sep. 2013 	\\
	Faculty of Mathematics, Informatics and Mechanics \\B.Sc. in Mathematics		\textit{minor:} Probability Theory 
\vspace{-2mm}

	\textbf{Warsaw School of Economics}, Poland   \hfill  Jan. 2012\\
	M.Sc. in Economics, \textit{major:} Macroeconomic Analysis
\vspace{-2mm}

 	\textbf{Warsaw School of Economics}, Poland  \hfill  Jul. 2009\\
   	B.Sc. in Economics, \textit{major:} Macroeconomic Analysis\\ 
    \textit{minor:} Computational and Optimisation Methods in Decision Making\\

\vspace{-5mm}
    
\section{\mysidestyle Visits and exchanges}
    \textbf{University of Edinburgh},  UK \hfill Apr. 2017 -- Jun. 2017\\
	Postgraduate Research Visit at the School of Mathematics\\ 
    Host Supervisor: Prof. Ruth King
  
    \vspace{-1mm}

	\textbf{University of G{\"o}ttingen}, Germany   \hfill Sep. 2010 -- Feb. 2011	\\
    Faculty of Economics and Business Administration \\M.Sc. programme, exchange within the Erasmus Programme
        

\vspace{-2mm}    
\section{\mysidestyle Publications}
{\mysidestyle Journals\vspace{1mm}}\\
\textit{\textbf{Neural network-based left ventricle geometry prediction from CMR images with application in biomechanics}},\\
	with Lukasz Romaszko, Alan Lazarus, David Dalton, Collin Berry, Xiaoyu Luo, Dirk Husmeier and Hao Gao\\
    \textit{Artificial Intelligence In Medicine}, 2021
\vspace{2 mm}\\
\textit{\textbf{Gaussian Process Enhanced Semi-Automatic ABC: Parameter Inference in a Stochastic Differential Equation System for Chemotaxis}},\\ 
    with Diana Giurghita and Dirk Husmeier\\
    \textit{Journal of Computational Physics}, 2020

\pagebreak

\textit{\textbf{Partially Censored Posterior for Robust and Efficient Risk Evaluation}}\\
	with Lennart Hoogerheide, Siem Jan Koopman and Herman K. van Dijk\\
	\textit{Journal of Econometrics}, 2020\vspace{2mm}\\ 
	%{\footnotesize [AI 96, \nth{3} in Google Scholar subcat.\ ``Probability \& Statistics with Applications'']}
	%
\textit{\textbf{Time-varying Combinations of Bayesian Dynamic Models and Equity Momentum Strategies}}\\
	with Nalan Ba\c{s}t\"{u}rk, Stefano Grassi, Lennart Hoogerheide and Herman K. van Dijk\\
	\textit{Journal of Econometrics}, 2018 \vspace{2mm} \\
	% {\footnotesize [AI 96, \nth{3} in Google Scholar subcat.\ ``Probability \& Statistics with Applications'']}
	%
\textit{\textbf{Bayesian Dynamic Modeling of High-Frequency Integer Price Changes}}\\
	with Istv\'{a}n Barra  and Siem Jan Koopman\\
	\textit{Journal of Financial Econometrics}, 2018\\ 
	% {\footnotesize [AI 89]}
\vspace{-5mm}

{\mysidestyle Conferences}  \vspace{1mm}\\	
\textit{\textbf{Inference in Cardiovascular Modelling Subject to Medical Interventions}}\\
	with Mihaela Paun, Mitchel J. Colebank, Mette S. Olufsen and Dirk Husmeier\\
	\textit{Proceedings of the International Conference on Statistics: Theory and Applications} 2021  \vspace{2mm}\\
	%
\textit{\textbf{Massive Dimensionality Reduction for the Left Ventricular Mesh}}\\
	with Lukasz Romaszko, Alan Lazarus, Hao Gao, Xiaoyu Luo and Dirk Husmeier\\
	\textit{Proceedings of the International Conference on Statistics: Theory and Applications} 2019  \vspace{2mm}\\
	%
\textit{\textbf{Direct Learning Left Ventricular Meshes from CMR Images}}\\
	with Lukasz Romaszko, Alan Lazarus, Hao Gao, Xiaoyu Luo and Dirk Husmeier\\
	\textit{Proceedings of the International Conference on Statistics: Theory and Applications} 2019 \vspace{1mm} \\

%
\vspace{-5mm}    
\section{\mysidestyle Submitted and under revision}	
%\section{\mysidestyle Working papers}	
\textit{\textbf{Semi-Complete Data Augmentation for Efficient State Space Model Fitting}}\\ 
    with Ruth King \\
    (revision for \textit{Journal of Computational and Graphical Statistics})\vspace{2mm} \\   
    %
\textit{\textbf{Efficient Bayesian Risk Estimation for Long Horizons}}\\
	with Lennart Hoogerheide and Siem Jan Koopman\\
	(submitted)\vspace{2 mm} \\ 
	%
\textit{\textbf{Bayesian Optimisation for Efficient Parameter Inference in a Cardiac Mechanics Model of the Left Ventricle}},\\ 
    with Hao Gao, Alan Lazarus and Dirk Husmeier \\
    (submitted) \\


%\vspace{-5mm}    		 	
%\section{\mysidestyle Ongoing \\Research } 
%   	\textit{\textbf{Bayesian Optimisation for Parameter Inference in Cardio-Mechanic Models}}\\ 
%    with Dirk Husmeier, Alan Lazarus, Hao Gao and Xiaoyu Luo \vspace{2mm} \\   	
%   	\textit{\textbf{Bayesian Risk Evaluation for State-Space Models}}\\ 
%    with Lennart Hoogerheide and Siem Jan Koopman  \\  
      
\vspace{-5mm}
 \section{\mysidestyle Service}
Reviewing for: \textit{Annals of Applied Statistics}, \textit{Journal of the Royal Society Interface}, \textit{Journal of Financial Econometrics}, \textit{Statistical Applications in Genetics and Molecular Biology},  \textit{Computational Economics}


%__________________________________________________________________________________________________________________
% \newpage	
\vspace{-2mm}

\section{\mysidestyle Selected Conference \\and Seminar \\Presentations \\ ([P]--poster)} 
	\textbf{British Applied Mathematics Colloquium (BAMC)},\\
	Glasgow, UK (online)\hfill 6-9 April 2021\vspace{1mm} \\
	\textbf{RSS Glasgow Local Group Event},\\
	Glasgow, UK (online)\hfill 9 February 2021 \vspace{1mm} \\
	\textbf{Statistics Seminar Series of the School of Mathematics and Statistics},\\
	Glasgow, UK (online)\hfill 29 January 2021 \vspace{1mm} \\
	\textbf{One World Approximate Bayesian Computation (ABC) Seminar},\\
	Warwick, UK (online)\hfill 29 October 2020\vspace{1mm} \\	
	\textbf{Seminar Series of the Division of Aerodynamics, Warsaw University of Technology},\\
	Warsaw, Poland\hfill 12 Dec. 2019 \vspace{1mm} \\
	\textbf{\nth{3} Annual Workshop on Financial Econometrics },\\
	{\"O}rebro, Sweden \hfill 11--12 Nov. 2019 \vspace{1mm} \\
	\textbf{\nth{10} European Seminar on Bayesian Econometrics [P]},\\
	St Andrews, UK \hfill 2--3 Sep. 2019 \vspace{1mm} \\
	\textbf{International Conference on Statistics: Theory and Applications},\\
	Lisbon, Portugal \hfill 13--14 Aug. 2019 \vspace{1mm} \\		
	\textbf{\nth{39} International Symposium on Forecasting},\\
	Thessaloniki, Greece \hfill 16--19 Jun. 2019 \vspace{1mm} \\
\newpage		
	\textbf{Workshop on Uncertainty Quantification for Cardiac Models [P]},\\
	Cambridge, UK \hfill 5--7 Jun. 2019 \vspace{1mm} \\		
	\textbf{Cside 2018 Conference}, Glasgow, UK \hfill 26 Nov. 2018 \vspace{1mm} \\
	\textbf{\nth{2} Joint Liverpool-Glasgow Maths Healthcare Centre Meeting},\\
	Liverpool, UK \hfill 30 Aug. 2018 \vspace{1mm} \\	
	\textbf{\nth{4} Bayesian Young Statisticians Meeting}, Warwick, UK \hfill 02 -- 03 Jul. 2018 \vspace{1mm} \\
	\textbf{\nth{12} Netherlands Econometric Study Group Meeting [P]}, \\
	Amsterdam, The Netherlands \hfill 25 May 2018  \vspace{1mm} \\ 
	\textbf{\nth{1} Bayes Comp [P]}, Barcelona, Spain \hfill 26-- 28 Mar. 2018 \vspace{1mm} \\
	\textbf{\nth{10} International Conference of the ERCIM WG on Computational}\\
	\textbf{and Methodological Statistics [P]}, London, UK\hfill 16-- 18 Dec. 2017 \vspace{1mm} \\ 	
	\textbf{\nth{8} European Seminar on Bayesian Econometrics},\\
	 Maastricht, The Netherlands\hfill 26--27 Oct. 2017 \vspace{1mm} \\ 
	\textbf{Sequential Monte Carlo Workshop 2017 [P]}, Uppsala, Sweden\hfill 30 Aug. -- 1 Sep. 2017 \vspace{1mm} \\ 
	\textbf{\nth{1} International Conference on Econometrics and Statistics},\\ Hong Kong \hfill 15--17 Jun. 2017 \vspace{1mm} \\ 
    \textbf{Statistics Seminar Series of the School of Mathematics},\\ Edinburgh, UK \hfill 19 May 2017 \vspace{1mm} \\ 
    \textbf{\nth{10} International Conference on Computational \\ and Financial Econometrics},  Seville, Spain\hfill 9--11 Dec. 2016  \vspace{1mm} \\ 
	\textbf{\nth{3} Bayesian Young Statisticians Meeting}, Florence, Italy \hfill 20--21 Jun. 2016  \vspace{1mm} \\ 
	\textbf{\nth{11} Netherlands Econometric Study Group Meeting [P]},\\
    Leuven, Belgium \hfill 17--18 Jun. 2016  \vspace{1mm} \\ 
%    \textbf{TI Ph.D. Lunch Seminar}, Amsterdam, The Netherlands \hfill 24 May 2016  \vspace{1mm} \\ 
%	\textbf{Econometrics Brown Bag Seminar}, Amsterdam, The Netherlands \hfill 21 Jan. 2016\\ 
  
\vspace{-5mm}

\section{\mysidestyle Selected Professional Research Experience}
\textbf{University of Warsaw}, Poland \vspace{0mm}\\
\textsl{Researcher} \hfill Feb. 2012 -- Sep. 2014\\
Pension system reform modelling within the OLG framework under time inconsistency; welfare analysis of various fiscal closures; numerical model solving in Fortran; paper writing and editing.\vspace{1.5mm} \\
%    \textbf{Civil Development Forum}, Warsaw, Poland \\
%    \textsl{Internship in the Analytical Department} \hfill Jul. 2010\\
%Analysis of the privatisation process in Poland; comparison of fiscal policy rules in selected EU countries; development of a database on fiscal stability reforms in the EU.\vspace{1.5mm} \\
\textbf{National Bank of Poland}, Warsaw, Poland \\
\textsl{Internship in the Economics Institute, Monetary Policy Strategy Bureau} \hfill Aug. 2009\\
Comparison and evaluation of the communication tools and institutional solutions implemented in selected central banks.  


\vspace{-1mm}
 

\section{\mysidestyle Project\\ Funding}	
   	\textbf{SofTMech Feasibility Fund} (10,000 GBP)	\hfill Jan. -- Mar. 2020\\
     co-investigator and co-supervisor (with Dirk Husmeier, Alan Lazarus and Hao Gao)\\
    A follow-up 3-month study on the 2019 project to employ a postdoc to develop a large-scale convolutional neural network for direct learning of 3D geometries from images as well as  to perform deep-learning based classification of medical images.  \vspace{1.5mm}\\ 
   	\textbf{SofTMech Feasibility Fund} (10,000 GBP)	\hfill Jan. -- Mar. 2019\\
     co-investigator and co-supervisor (with Dirk Husmeier and Hao Gao) \\
    A 3-month project employing a postdoc to investigate the usefulness of deep learning techniques for dimensionality reduction of 3D geometries and for direct learning these geometries from image data.
    
\vspace{-1mm}
 
%\newpage
\section{\mysidestyle Travel Grants,\\Awards and \\ Scholarships}	
   	\textbf{\"{O}rebro University School of Business travel funding} (650 EUR) \\
    to attend Workshop on Financial Econometrics, \"{O}rebro, Sweden
   	\hfill Sep. 2019 \vspace{1.5mm} \\    	\textbf{International Institute of Forecasters travel award} (1660 USD)\\
    to attend ISF 2019 and the forecasting summer school% 1660 USD
   	\hfill Mar. 2019 \vspace{1.5mm} \\ 
   	\textbf{Cside 2018 \nth{1} place  prize} (250 GBP) \\
   	for 2 subcompetitions for SDE models% 250 GBP
   	 \hfill Nov. 2018 \vspace{1.5mm} \\ 
   	\textbf{ISBA travel award to attend BAYSM 2018} (400 USD)  \hfill Apr. 2018 \vspace{1.5mm} \\ %\\ BAYSM 2018 organizing committee,% 400 USD 
   	%\hfill Apr. 2018 \vspace{1.5mm} \\ 
   	\textbf{SMC 2017 scholarship} (15,000 SEK $\approx$ 1600 EUR)\hfill Aug. 2017  \\  to attend the SMC 2017 workshop and the intensive course \vspace{1.5mm}\\ %\\ SMC2017 organizing committee %15,000 SEK 
   %	\hfill Aug. 2017 \vspace{1.5mm} \\   
\newpage
   	\textbf{Tinbergen Institute merit-based scholarship} (30,000 EUR) \\ 
   	Tinbergen Institute, full scholarship, 2 years of MPhil% 30,000 EUR 
   	\hfill Sep. 2013 -- Aug. 2015\vspace{1.5mm} \\   	   	
       \textbf{Student Exchange Scholarship}\\  Warsaw School of Economics, the LLP Erasmus \hfill Sep. 2010 -- Feb. 2011\vspace{1.5mm} \\
       \textbf{Scholarship for excellent academic achievements}\\ Warsaw School of Economics \hfill Oct. 2007 -- Sep. 2010 
       
%__________________________________________________________________________________________________________________
%\newpage	
%\vspace{-1mm}
 
 \section{\mysidestyle Teaching Experience}
    \textbf{University of Glasgow}, UK\\ 
    \textit{Honours and MSc Projects supervision} (Statistics)  \hfill 2018--2021 \vspace{2mm}\\  	
    \textbf{VU Amsterdam}, the Netherlands \\ 
    TA for \textit{Econometrics II} (B.Sc. course)  \hfill Feb. -- Mar. 2017\\  	
    TA for \textit{Business Mathematics} (B.Sc. course, evaluation: 3.8/5)  \hfill Sep. -- Oct. 2016\\ 
    TA for \textit{Business Statistics} (B.Sc. course, evaluation: 4.1/5)  \hfill Feb. -- Mar. 2016\vspace{2mm}\\
   	\textbf{Tinbergen Institute}, Amsterdam, the Netherlands \\
    TA for \textit{Advanced Econometrics II} (M.Phil. course, evaluation: 4.1/5) \hfill Jan. -- Feb. 2015\\      
	TA for \textit{Measure Theory and Stochastic Processes} (M.Phil. course, evaluation: 4.2/5) \hfill Sep. -- Oct. 2014\\

\vspace{-5mm}

\section{\mysidestyle Additional\\ Courses \\and Trainings} 
	\textbf{Forecasting Summer School}\\
        Thessaloniki, Greece\hfill Jun. 2019\\
        Probabilistic forecasting (scoring rules, combining predictive distributions)\vspace{1.5mm} \\	
	\textbf{Scalable Bayesian Inference}\\
        Edinburgh, UK\hfill Jun. 2018\\
        Scalable algorithms for large datasets (embarrassingly parallel MCMC, approximate MCMC),\\ scalable Bayesian methods for very high-dimensional data analysis\vspace{1.5mm} \\	
        %                                 
	\textbf{Workshop on Machine Learning Models and Methods for Econometricians}\\
        Maastricht, The Netherlands\hfill Oct. 2017\\
        Gaussian processes, distributed and subsampling MCMC, variational Bayes,  deep learning\vspace{1.5mm} \\	
	\textbf{Intensive PhD level course on Sequential Monte Carlo Methods}\\
        Uppsala University, Sweden\hfill Aug. 2017\\
        Particle MCMC, high-dimensional filtering, SMC for probabilistic graphical models and probabilistic programming\vspace{1.5mm} \\   
       %
	\textbf{Reading Group on Bayesian Nonparametrics}\\
        University of Edinburgh, UK \hfill May -- Jun. 2017\\
        Introduction to Dirichlet process and their mixtures, Bayesian nonparamteric regression\vspace{1.5mm} \\
	\textbf{Course on High Performance Computing}\\
        VU Amsterdam, The Netherlands \hfill Oct. 2016\\
        Basics of Unix and cluster computing,  Hadoop and data analytics, GPU programming, HPC cloud\vspace{1.5mm} \\
%     \textbf{TI Econometrics Lectures 2015}, Rotterdam, The Netherlands \hfill \textbf{June 2015}\\ 
%   \textit{Structural Modelling of Economic Time Series} \\ Participation in the lecture 
%   
%        \textbf{TI Economics Lectures 2015}, Amsterdam, The Netherlands \hfill \textbf{May 2015}\\ 
% \textit{New Style Central Banking}\\
% Participation in the lecture
%
%     \textbf{TI Econometrics Lectures 2014}, Rotterdam, The Netherlands \hfill \textbf{June 2014}\\ 
%   \textit{The Econometric Analysis of Recurrent Events in Economics and Finance} \\ Participation in the lecture (final grade: 9)
%   
%        \textbf{TI Economics Lectures 2014}, Amsterdam, The Netherlands \hfill \textbf{June 2014}\\ 
% \textit{Markets with Asymmetric Information}\\
% Participation in the lecture (final grade: 8)
%   
%        \textbf{18th International Conference on Macroeconomic Analysis and International Finance} University of Crete, Rethymno, Greece \hfill \textbf{May 2014} \\ 
%   Participation in the conference as a co-author of a presented paper
%
%        \textbf{Current Trends in Macroeconomic and Finance Research},\\  National Bank of Poland, Warsaw, Poland  \hfill \textbf{July 2012}\\ 
%  Participation in the economics workshop
%
        \textbf{Summer School in Applied Macroeconomics}\\
        University of Salento, Lecce, Italy \hfill Jul. 2012\\
        Programming in Matlab,  VAR for monetary policy, state space models and the Kalman Filter%
%23 - 27 July 2012
%        \textbf{DSGE and beyond –- expanding the paradigm in monetary policy research?}\\  National Bank of Poland, Warsaw, Poland \hfill \textbf{September 2011}\\ 
%  Participation in the conference
 
%        \textbf{Introduction to Stata}, University of G{\"o}ttingen, Germany \hfill \textbf{December 2010} 	\\
%        Block course covering basic commands, data management, graphs, data manipulation, descriptive statistics, regression analysis and basic programming in Stata.

%        \textbf{SQL course}, University of G{\"o}ttingen,  Germany \hfill \textbf{November 2010} \\ 
% Principles of  relational databases  and SQL queries.


%  \newpage
%   __________________________________________________________________________________________________________________
% \newpage	
 
 	

    % Computer Skills
   \section{\mysidestyle Computer\\ Skills} 
   Strong experience in MATLAB, R, Fortran   \vspace{1mm}\\
   Some experience with Python, C/C++, BUGS/JAGS \vspace{1mm}\\
	Familiarity with EViews, Stata, SPSS \vspace{1mm} \\
 %   Databases:	EcoWin, Reuters \vspace{1mm}\\
	Other: \LaTeX, Linux, GitHub  

    % Foreign Languages
   \section{\mysidestyle Language\\ Skills}  
	Polish (native), English (fluent),  German (good command),    \\
    Russian (intermediate),  French (basic),  Dutch (basic)

\newpage	     
\section{\mysidestyle References} 

\noindent
\begin{minipage}[t][6cm][t]{\dimexpr0.5\textwidth-0.5\Colsep\relax}
\textbf{Prof. Siem Jan Koopman} \\    
Department of Econometrics and OR\\
Vrije Universiteit Amsterdam, \\ \url{s.j.koopman@vu.nl}
\vspace{5mm}

\textbf{Dr Lennart Hoogerheide} \\  
Department of Econometrics and OR \\  
Vrije Universiteit Amsterdam,\\ \url{l.f.hoogerheide@vu.nl}
\vspace{5mm}

\textbf{Prof. Herman K. van Dijk} \\  
Econometric Institute,\\  
Erasmus University Rotterdam,\\ \url{hkvandijk@ese.eur.nl}
\end{minipage}
\hfill
\begin{minipage}[t][6cm][t]{\dimexpr0.5\textwidth-0.5\Colsep\relax}
\textbf{Prof. Dirk Husmeier} \\    
School of  Mathematics and Statistics\\
University of Glasgow,\\ \url{Dirk.Husmeier@glasgow.ac.uk}
\vspace{5mm}

\textbf{Prof. Ruth King} \\  
School of Mathematics,\\  
The University of Edinburgh,\\ \url{ruth.king@ed.ac.uk}
\vspace{5mm}



\end{minipage}


%______________________________________________________________________________________________________________________
\end{resume}
\end{document}
